Correcting K-correction: dark energy is based on a math error from 1930

### 2025-02-07 paper/dark_energy_corrections.tex

@@

In order to use SNe Ia to estimate the expansion rate of the universe, we need to
identify both the redshift $z$ and the light travel distance $d$. In order to
compute the light travel distance $d$, we use the definition of the distance
modulus \citep{weinberg2008}:

\begin{equation}
\label{eq:mu_def}
  d = 10^{1 + (m - M)/5} \text{pc}.
\end{equation}

@@

@@

\noindent In other words, the goal of the K-correction equation is to remove
all redshift effects from the apparent magnitude $m$ so that the distance
modulus defined in Equation \ref{eq:mu_def} allows us to compute the light
travel distance $d$.

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{distance_vs_redshift.pdf}
  \caption{The relationship between light travel distance and redshift for two
  treatments of the magnitude data. The red $k(z) = 1$ treatment, which represents
  the uncorrected values, is clearly non-linear while the blue $k(z) = 1 + z$
  treatment, which fixes the K-correction redshift error, appears to be linear.
  The displayed points are roughly a third of the values in the full SNe Ia
  dataset published in \citet{abbott2024}, selected with uniform redshift
  spacing to aid visibility. }
  \label{fig:distance_vs_redshift}
\end{figure}

>>>>

@article{lesser2015,
  title={A summary of charge-coupled devices for astronomy},
  author={Lesser, Michael},
  journal={Publications of the Astronomical Society of the Pacific},
  volume={127},
  number={957},
  pages={1097--1104},
  year={2015},
  publisher={The Astronomical Society of the Pacific}
}
\end{filecontents}

@@

In order to use SNe Ia to estimate the expansion rate of the universe, we need
to identify both the redshift $z$ and the light travel distance $d_{LT}$. In
order to compute the light travel distance $d_{LT}$ in parsecs (pc), we use the
definition of the distance modulus \citep{weinberg2008}:

\begin{equation}
\label{eq:mu_def}
  d_{LT} = 10^{1 + (m - M)/5} \text{pc}.
\end{equation}

@@

Cosmology uses multiple distance measurements, but for measuring the expansion
rate of the universe, the only one we care about is the light travel distance
$d_{LT}$. A similar distance measurement, the luminosity distance $d_L$, is
often discussed in conjunction of flux measurements, but $d_L$ represents an
illusory distance. In fact, ${d_{L} = d_{LT} \times (1 + z)}$, which can be
thought of as the distance an object would need to be to produce the same
amount of measured energy flux if redshift did not exist. The light travel
distance $d_{LT}$ represents a physical quantity while $d_{L}$ does not.

@@

\noindent In other words, the goal of the K-correction equation is to remove
all redshift effects from the apparent magnitude $m$ so that the distance
modulus defined in Equation \ref{eq:mu_def} allows us to compute the light
travel distance $d_{LT}$.

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{distance_vs_redshift.pdf}
  \caption {The relationship between light travel distance $d_{LT}$ and
  redshift $z$ for two treatments of the magnitude data. The red ${k(z) = 1}$
  treatment, which represents the uncorrected values, is clearly non-linear
  while the blue ${k(z) = 1 + z}$ treatment, which fixes the K-correction
  redshift error, appears to be linear.  The displayed points are roughly a
  third of the values in the full SNe Ia dataset published in
  \citet{abbott2024}, selected with uniform redshift spacing to aid visibility.
  }
  \label{fig:distance_vs_redshift}
\end{figure}
